\section{Some Measure Theoery}

First we want to begin with background definitions and theorems.  Erd\"{o}s' problem specifically deals with infinite set, and affine copies found in measurable set of sets.  In our problem, rather than dealing with measurable sets, we will instead use the set of dense $G_\delta$ sets.  

Underpinning the nuances of this problem, measure theoretic size, and topological size, are not the same. From an intuitive sense of the number line one might think when you are scattered throughout an interval, you would have measure, except in special cases. Similarly one might think that if you have measure, then you would be scattered everywhere.  However both of these instances fail when you add in rigorous arguments.  Indeed it is possible to construct a set that is no-where dense and have positive measure.  It is also possible to construct an uncountable set that is be dense and has zero measure. In other words topological size (density) is not the same thing as measure theoretic size. 

First we will review some measure theory.  In order to define \textit{measure} and \textit{measurable sets} we first need to define $\sigma$\hyphen{Algebra.   



\begin{definition}[$\sigma$-Algebra]
    Let $X$ be some set and $2^X$ be the set of subsets of $X$. Let $\Sigma \subseteq 2^X$. We call $\Sigma$ a $\sigma-$algebra over $X$ if it satisfies the following three conditions:
    \begin{enumerate}
        \item $\emptyset \in \Sigma$
        \item If $E \in \Sigma$, then $X\setminus E \in \Sigma$. 
        \item If $E_1, E_2, \dots \in \Sigma$ is a sequence of subsets, then $\bigcup_{k=1}^\infty E_k \in \Sigma$. 
    \end{enumerate}
\end{definition}

In this instance we describe set of sets in terms of inersection and union.  This allows us to generate an algebraically closed colleciton of sets.  Now if we have a base definition of measure, we are also able to contruct our colleciton of sets, on which measure is defined.   

\begin{definition}[Measure]
    Let $X$ be a set and $\Sigma$ be a $\sigma-$algebra over $X$.  A function $\mu: \Sigma \to \{\R \cup \infty\}$ is called a measure if it satisfies the following properties:
    \begin{enumerate}
        \item \textbf{Non-negativity}: for all $E \in \Sigma$, $\mu(E)\geq 0$.
        \item \textbf{Null empty set}: $\mu(\emptyset) = 0$. 
        \item \textbf{Countable Additivity} ($\sigma$-additivity): For all countable collections $\{E_k\}_{k=1}^\infty$ of pairwise disjoint sets in $\Sigma$, $$\mu\left( \bigcup_{k=1}^\infty E_k \right) = \sum_{k=1}^\infty \mu(E_k).$$
    \end{enumerate}
\end{definition}

In this instance, a measurable set 
\begin{definition}[Measurable Set]
    Let $(X,\Sigma)$ be a measurable space.  A set $S\subseteq X$ is a \textit{measurable set} if and only if $S \in \Sigma$.
\end{definition}
Note that a non-measurable set is a set that is not in the $\sigma$-algebra.  That is to say not all sets are necessarily measurable.  Nonmeasurable sets fall outside of our work.  

% \begin{example}[The Vitali Set is not Lebesgue-measurable.]
%     Consider the following equivalence relation on $\R$: 
%     $$ x\sim y \iff x-y \in \Q.$$  This is the same as the quotient group $\R \diagup \Q$.  

%     Notice for a moment that every single element in $\R \diagup \Q$  intersects with some element of $[0,1]$ because the $\pmod{1}$ operation is subtraction by an integer.  Therefore there is a subset of $[0,1]$ that contains exactly one representative of each element of $\R \diagup \Q$.
%     By the axiom of choice, define the Vitali set $V$ as the set of distinct representatives in $[0,1]$, one from each equivalence class. 
%     \begin{claim}The Vitali set $V$ is not Lebesgue measurable.
%     \end{claim}
%     \begin{proof}
        
    
%     Assume for the same of contradiction, that $V$ is measurable.
%     Consider the set of translations of $\{V_q\}$ $\pmod{1}$ , where for each $q \in \Q\cap[0,1)$, $$V_q = \{v+ q \pmod{1}: v \in V\}.$$   

%     Because measure is translation invariant, then each $V_q$ is also measurable.  Notice that the set $\{V_q\}$ is a countable family of pairwise disjoint sets such that 
%     $$\bigcup_{q \in \Q} V_q = [0,1].$$ 
%     Again because it is countable and pairwise disjoint, this implies that 
%     \begin{equation}\label{eqn:vitineq}
%         \big\vert [0,1] \big\vert = \sum \vert V_q\vert = \sum_{k = 1}^\infty V.
%     \end{equation}
%     By assumption $V$ is measurable, however the sum of a constant non-negative number is either $0$ or $\infty$, and $\vert [0,1]\vert \neq 0,$ and $\vert [0,1]\vert \neq \infty$.  Therefore our assumption is false and $V$ is not Lebesgue measurable.  
%     \end{proof}
  
% \end{example}
%Define uncountable and dense 

We will also need to define \textit{uncountable} and \textit{dense}.  First we start with \textit{countable}.

\begin{definition}[Countable]
    A set $X$ is called \textit{countable} if for some  subset $N \subset \N$, that is not necessarily finite, there exists a bijection $f: X \to N$.  
\end{definition}

\begin{definition}[Uncountable]
    A set $X$ is called \textit{uncountable}, if it is not \textit{countable}.
\end{definition}

We also need to define \textit{dense}.  There are many equivalent definitions of dense.  We will use the following definition so that we can continue to develop the intuion around intervals and interiors. 

\begin{definition}[Dense]
    A set $S$ is called dense in $X$ if for every $x \in X$, every neighborhood $U$ of $x$ intersects $A$.  
\end{definition}


In a similar fashion to the definitions of \textit{countable} and \textit{uncountable}, the oppsite of \textit{dense} is \textit{nowhere dense}.

\begin{definition}[Nowhere Dense]  Let $X$ be a topological space.  A subset $B \subseteq X$ of a topological space is called \textit{nowhere dense} in $X$ if its closure has an empty interior.  That is to say, $B$ is \textit{nowhere dense} in $X$ if for each open set $U\subseteq X$, $B\cap U$ is not dense in $U$.      
\end{definition}


This allows us to now explore the differences between density and measure.  As stated earlier, topological size and measure theoretic size are not necessarily related.  What do we mean by topologically Large? Uncountable and dense.  Similarly what do we mean by measure theoretically large?  Non-zero measure.  After reviewing t It is helpful to define the opposite of topologically large, namely meager sets.



\begin{definition}[Meager]  A subset $C \subseteq X$ of a topological space is called \textit{meager} in $X$ if it is the countable union of nowhere-dense subsets of $X$.    
\end{definition}
Now we look at our example.  
\begin{example}A measure theoretically large set is not necessarily topologically large.

Consider the interval $[0,1]$ and for all positive integers $a,n \in \N$ remove the intervals $(\frac{a}{2^n} - \frac{1}{2^{n+1}},\frac{a}{2^n} + \frac{1}{2^{n+1}})$.  Notice that the intervals are a geometric series and for each $n$ add up to at most $\frac{1}{2^{n+1}}$.  Therefore the set 
$$[0,1] \setminus \bigcup_{a,n \in \N} \left(\frac{a}{2^n} - \frac{1}{2^{n+1}},\frac{a}{2^n} + \frac{1}{2^{n+1}}\right),$$
is closed, has an empty interior, and is of positive measure.  
\end{example}

Next we will define dense $G_\delta$ sets, as well as some useful examples.  
\begin{definition}[G-Delta Set]
    A $G_\delta$ set is the countable intersection of open sets.  Namely, let $O_i \subset X$ for $i \in \N$ be a collection of open sets of $X$.  Then 
    $\bigcap_{n=1}^\infty O_i,$ is a $G_\delta$ set.  
\end{definition}

\begin{example}
    The irrational numbers are a $G_\delta$ set.  Consider the following construction of the set of irrational numbers:
    $$\R \setminus \Q = \bigcap_{q \in \Q}\R \setminus \{q\}.$$
\end{example}
Notice that each $\R\setminus \{q\} = (-\infty, q) \cup (q, \infty)$ is an open subset of $\R$.  Furthermore, rational numbers are countable.  Therefore the intersection of these sets are a $G_\delta$ set.  Moreover, in this instance it is a dense $G_\delta$ set.  We will study these objects further.  

Lastly we remark that there is an analogous set which is the countable union of closed sets.
\begin{definition}[F$_\sigma$ Set]
    An $F_\sigma$ set is the countable union of closed sets.  This is equivalent to the compliment of a G-delta is an F-sigma set.  
\end{definition}

%measure big topological small
%topologically big (dense g_delta), measure small 