%\documentclass{article}

%this is optional!!!

%\begin{document}

I want to take a moment to thank a few people who have shaped my pursuit of math.  First, thank you Dr. Chun-Kit Lai.  I remember my first class in analysis with you.  I have learned so much from you and have grown from working with you.  You have been a true teacher, mentor, and friend.  

I also want to name several other professors.  Dr. Arek Goetz, my time at SFSU started with your online calculus course and a recommendation for the Math program. It is so fitting that you are also teaching me my last course at SFSU.  Dr. Emily Clader, you have taught me about the subtleties of math, the subtleties of explanation, and how they are not the same thing! You have also done this while encourage a greater diversity in perspectives and collaboration.  You have also pointed out my excessive use of commas.  Dr. Dusty Ross, your bonus problems sparked my interest in topology and you encouraged me to take my first topology course with Dr. Clader.  

Thank you Mom and Dad for supporting me.  Mom, you sat with me at the dinner table, where we did puzzles about shapes, volumes, and space.  At the same time your fearlessness, your drive for your own career, and your love of our family has inspired my own path for learning.  Dad, you taught me about sizes of infinity and the power of listening to and understanding others.  Both of you continue to push the limits of my imagination. 

%To my siblings, this is all your fault.  
%You pushed me into subtraction when I only knew addition.  You pushed me into negative numbers when I only knew subtraction.  Worse still you pushed me into exponents, negative exponents, and fractional exponents, when I only knew multiplication!  
%I have learned from you all that math is the joy of confusion and surprise.  Now when I explain math I can ask you, "Do you get it?"

Patrick O'Melveney, I am so glad we have become friends through such unlikely circumstances.  You have helped me better understand math and myself.  

Finally, thank you to my wife.  Kim, you tell it like it is.  You help me see things as they are.  You gave me the courage to go to graduate school and the support to stay in graduate school.  For that I am more grounded and supported. 



%\end{document}
